### 2014-09-05 tex/proofs.tex
Updated soundness portion of the field write proof.

It remains to show that $\mathbb{S}( \phi_s^\prime \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime) )$. For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(s_\ell^prime \rightharpoonup_{h} s_s^\prime)$, and therefore the satisfiability cannot be changed. For locations in Class 2 or Class 3, the new constraints take either the form $\phi_x \wedge \phi_{orig}$, or $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$. Constraints of the form  $\phi_x \wedge \phi_{orig}$ contain terms $\phi_x$ and $\phi_{orig}$ which were already conjoined to prior heap constraint, so satisfiability is not affected. In constraints of the form $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$, the term $\phi_x$ is conjoined to the prior heap constraint, and all the other terms involve the new variable $r_f$, so satisfiability is not affected. Since the previous heap constrain is satisfiable, and none of the new terms can impact the satisfiability, we know that the new heap constraint must also be satisfiable.

@@

%proof for field write
\begin{lemma}[Exactness of Field Write Rule]
\label{lem:write}
If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then $s_s^\prime$ is equal to $ \lp \cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \eta\ \cfgnt{k}\rp$ and is exact with respect to $s_0$ and $\pi_n \ (\eta\ \cfgnt{k}\ \emptyset)$:
$$s_\ell^\prime \sqsubset s_s^\prime \Leftrightarrow s_\ell^\prime \in \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) ) $$

@@

The first step is to show that $s_s^\prime$ is complete with respect to the feasible set. Take any lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$, and find state $s_\ell^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$. Let $l_\ell$ be the location such that $\{(\phi\ l_\ell )\} = \cfgnt{L}_\ell(\cfgnt{r}_x) $ for some $\phi$. To show that $s_\ell^\prime \sqsubset s_s^\prime$, we need to demonstrate that there exists a function $h^\prime$ such that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$, and that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$. Since $s_h \sqsubset s_s$, we know that there exists a function $h$ such that $s_\ell \rightharpoonup_{h} s_s$. Let $h^\prime = h$.

To see that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$, we must consider how $s_s^\prime$ is constructed. Let $l_\alpha$ and $l_\beta$ be arbitrary locations in $\cfgnt{L}_{\ell^\prime}^\rightarrow$ such that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f ))$, let $\theta = \cfgnt{L}_s(\cfgnt{R}_s(h(l_\ell),f))$, and let $\theta^\prime =   \cfgnt{L}_s^\prime(\cfgnt{R}_s^\prime(h(l_\ell),f))$.

@@

On the other hand, suppose $l_\beta = l_\ell$. In this case we know that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\ell,f ))$. From the lazy field rule, we can surmise that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell}(\cfgnt{r} )$, and since $s_\ell \sqsubset s_s$, we know that$(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s}(\cfgnt{r})$ for some constraint $\phi_b$. Using this fact, we can apply the summary Field Write rule to infer that $l_\alpha$ must be one of the locations in $\theta^\prime$, and therefore $(\phi_c\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}^\prime(l_\ell,f))$

@@

Observe that the field write rule places every possible target value into the reference stored at the target location. Thus, whatever the write value was for $s_i^\prime$ was, it was written to the target field, meaning $s_i^\prime$ is represented by $s_s^\prime$.

To show that $s_s^\prime$ is exact with respect to the feasible set, we use the same argument as in the field read proof: that because $s_s^\prime$ represents every state in the feasible set, and since the cardinality of the set of states represented by $s_s^\prime$ is less than or equal to the cardinality of the feasible set, that $s_s^\prime$ can only represent feasible states.

>>>>

It remains to show that $\mathbb{S}( \phi_s^\prime \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime) )$. For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(s_\ell^\prime \rightharpoonup_{h} s_s^\prime)$, and therefore the satisfiability cannot be changed. For locations in Class 2 or Class 3, the new constraints take either the form $\phi_x \wedge \phi_{orig}$, or $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$. Constraints of the form  $\phi_x \wedge \phi_{orig}$ contain terms $\phi_x$ and $\phi_{orig}$ which were already conjoined to prior heap constraint, so satisfiability is not affected. In constraints of the form $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$, the term $\phi_x$ is conjoined to the prior heap constraint, and all the other terms involve the new variable $r_f$, so satisfiability is not affected. Since the previous heap constrain is satisfiable, and none of the new terms can impact the satisfiability, we know that the new heap constraint must also be satisfiable.

@@

%proof for field write
\begin{lemma}[Exactness of Field Write Rule]
\label{lem:write}
If $s_s \cong \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n )$ for some symbolic state $s_s$, initial state $s_0$, and control flow path $\pi_n$, and if $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then:
$$s_\ell^\prime \sqsubset s_s^\prime \Leftrightarrow s_\ell^\prime \in \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) ) $$

@@

The first step is to show that $s_s^\prime$ is complete with respect to the feasible set. Take any lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$, and find state $s_\ell^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$. Let $l_\ell$ be the location such that $\{(\phi_a\ l_\ell )\} = \cfgnt{L}_\ell(\cfgnt{r}_x) $ for some $\phi_a$. To show that $s_\ell^\prime \sqsubset s_s^\prime$, we need to demonstrate that there exists a function $h^\prime$ such that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$, and that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$. Since $s_h \sqsubset s_s$, we know that there exists a function $h$ such that $s_\ell \rightharpoonup_{h} s_s$. Let $h^\prime = h$.

First, we consider how $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$. Let $l_\alpha$ and $l_\beta$ be arbitrary locations in $\cfgnt{L}_{\ell^\prime}^\rightarrow$ such that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f ))$, let $\theta = \cfgnt{L}_s(\cfgnt{R}_s(h(l_\ell),f))$, and let $\theta^\prime =   \cfgnt{L}_s^\prime(\cfgnt{R}_s^\prime(h(l_\ell),f))$.

@@

On the other hand, suppose $l_\beta = l_\ell$. In this case we know that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\ell,f ))$. From the lazy field rule, we can surmise that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell}(\cfgnt{r} )$, and since $s_\ell \sqsubset s_s$, we know that $(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s}(\cfgnt{r})$ for some constraint $\phi_b$. Using this fact, we can apply the summary Field Write rule to infer that $l_\alpha$ must be one of the locations in $\theta^\prime$, and therefore $(\phi_c\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}^\prime(l_\ell,f))$

@@

By proving the existence of a valid homomorphism, we have shown that if $s_\ell \sqsubset s_s$, $s_\ell \rightarrow_\ell s_\ell^\prime$, and $s_s \rightarrow_s s_s^\prime$, then $s_\ell^\prime \sqsubset s_s^\prime$. Since $s_s \cong \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n )$, and since $\pi_n (\eta\ \cfgnt{k}\ \emptyset)$  is the only possible control flow sequence from state $s_s$ or any state $s_\ell$ where $s_\ell \sqsubset s_s$, we may deduce that $\{ s_\ell^\prime | \exists s_\ell (s_\ell \sqsubset s_s \wedge s_\ell \rightarrow_\ell s_\ell^\prime ) \} = \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) )$. Therefore, $s_\ell^\prime \in \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$. This concludes the proof of completeness.

To show that $s_s^\prime$ is sound with respect to the feasible set, we use the same argument as in the field read proof: that any state $s_\ell^\prime$ represented by $s_s^\prime$ must have a counterpart state $s_\ell$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$ and $s_\ell \sqsubset s_s$. Because $s_s$ is exact, $s_\ell^\prime$ must be a part of the feasible set.
